---
title: "Weight of Fish"
author: "Racheal Adeneye"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(car)
require(leaps)
```

# Predicting Fish Weight
```{r}
fish <- read.csv(file = "Fish.csv")
```

```{r eval=TRUE}
 
fish <- fish %>%
mutate(across(where(is.character), as.factor))
levels(fish$Species)
Bream <- filter(fish, Species == "Bream")
Bream <- select(Bream, -Species) 
Parkki <- filter(fish, Species == "Parkki")
Parkki <- select(Parkki, -Species) 
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -Species) 
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -Species) 
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
Smelt <- filter(fish, Species == "Smelt")
Smelt <- select(Smelt, -Species) 
Whitefish <- filter(fish, Species == "Whitefish")
Whitefish <- select(Whitefish, -Species) 
```

# For each of the three species of fish listed below, determine the best regression model and also the best 2 element regression model. Use the BestSubset Regression helper file.


## Perch
```{r}
library(leaps)
regsubsets.out <-
  regsubsets(Weight ~.,
                             data=Perch,
                             nbest=1,
                             force.in=NULL,force.out=NULL,
                             method="exhaustive")
summary.out<-summary(regsubsets.out)
as.data.frame(summary.out$outmat)

```

```{r}
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottom",main="adjustedR^2")

```

### Best Models
As we look at the given data, we can infer that the best model is the two-element model(the H-W models).

### Best Two regressor model
The best two regressor model would also be the H-W models

## Pike
```{r}
library(leaps)
regsubsets.out <-
  regsubsets(Weight ~.,
                             data=Pike,
                             nbest=1,
                             force.in=NULL,force.out=NULL,
                             method="exhaustive")
summary.out<-summary(regsubsets.out)
as.data.frame(summary.out$outmat)

```

```{r}
library(car)
subsets(regsubsets.out,statistic="adjr2",legend = "bottom",main="adjustedR^2")


```

### Best Models
The best model to use here is the 5-element model (L1-L2-L3-H-W models).

### Best Two regressor model
The best two regressor model in this case is the L1-L3 models. Since the best model is different from the best two regressor model, we must run an ANOVA test.

```{r}
model5 <- lm(Weight~ . ,data=Pike)
summary.lm(model5)
model2=lm(Weight~ .  -Length2-Height-Width, data=Pike)
model3=lm(Weight~ .  -Length2-Height-Width, data=Pike)
anova(model5,model2)

```

## Roach
```{r}
library(leaps)
regsubsets.out <-
  regsubsets(Weight ~.,
                             data=Roach,
                             nbest=1,
                             force.in=NULL,force.out=NULL,
                             method="exhaustive")
summary.out<-summary(regsubsets.out)
as.data.frame(summary.out$outmat)

```

```{r}
library(car)
subsets(regsubsets.out,statistic="adjr2",legend= "bottomleft",main="adjustedR^2")
```

### Best Models
The best model to use here is the L3-W models (model 2).

### Best Two regressor model
The best two regressor model to use here is also the L3-W models (model 2).

## Final Summary Statements